HiC Contact Map Comaprison Using Graphlet Approach

### 2018-10-16 papers/manuscripts/manuscript.tex
save

Here, we present local structural analysis between
4 sets of Hi-C data. All four data sets are sequences
from the same cell line, with one of them being
a normal cell and the other three sequenced from
three types of leukemic cells. In order to achieve
this, we used graphlets, given their strength in
capturing information about local structures of
a graph. We first thresholded Hi-C interaction frequency
matrices in order to convert in to an unweighted undirected
graph adjacency matrix. We the extracted counts of
the first 73 orbits for each node, identifying each
node with a signature vector of size 73. We then
applied graphlet distance metrics proposed in
{prvzulj2007biological} together with statistical methods
in order to find difference between cell lines.
Our results show that difference of local structure
between normal cells and leukemic cells are significantly
larger that difference between cancer-cancer cells.

@@

\subsection{Graphlets and Orbits}
\begin{figure}[H]
    \centering
    \includegraphics[width=.5\textwidth]{figures/graphlets.png}
    \caption{}
    \label{fig_graphlets}
\end{figure}
Recently, graphlet comparison has emerged as
a novel method for comparing large networks in
order to find local similarities in them. A
graph G is a pair $(V,E)$, where $V$ is a set of
vertices and $E \subseteq V\times V$ is a set of
edges. A connected graph is one where there is
a path between every pair of vertices.
Given a graph $G(V, E)$ and $S \subseteq V$,
then $G'(S, E')$ is a graphlet if and only if
it is connected $E' = \{(u, v) | u, v \in V \quad \&
\quad (u, v) \in E \rightarrow (u, v) \in E'\}$. 
There a total of 30 graphlets
of size 2, 3, and 5.  Figure \ref{fig_graphlets}
demonstrates these graphlets. 
As can be seen there is only one graphlet
of size 2 which is equivalent to an edge; that
is, the number of graphlet 1 in a graph is the
same as the number of edges on the graph. There
are also a total of 2 graphlets of size 2, 6
of size 4 and 20 of size 5. The nodes of each graphlet
can be partitioned into sets of topographically equivalent
nodes called orbits. For  example, in  Figure 
\ref{fig_graphlets}, we can see that G3 can be
partitioned into 2 sets of nodes, the middle ones
(white) and the outer nodes (black). 
For the same set of graphlets,
there are 73 orbits that are also illustrated in
figure  Figure using nodes of difference shades.

>>>>

Here, we present local structural analysis between
4 sets of Hi-C data. All four data sets are sequences
from the same cell line, with one of them being
a normal cell and the other three sequenced from
three types of leukemic cells. In order to achieve
this, we used graphlets, given their strength in
capturing information about local structures of
a graph. We first thresholded Hi-C interaction frequency
matrices in order to convert in to an unweighted undirected
graph adjacency matrix. We the extracted counts of
the first 73 orbits for each node, identifying each
node with a signature vector of size 73. We then
applied graphlet distance metrics proposed in
\cite{prvzulj2007biological} together with statistical methods
in order to find difference between cell lines.
Our results show that difference of local structure
between normal cells and leukemic cells are significantly
larger that difference between cancer-cancer cells.

@@

\subsection{Graphlets and Orbits}
\begin{figure}[H]
    \centering
    \includegraphics[width=.5\textwidth]{figures/graphlets.jpg}
    %\includegraphics[width=.5\textwidth]{/home/bzr0014/Dropbox/graphlets.png}
    %\includegraphics[width=.5\textwidth]{/home/bzr0014/Dropbox/graphlets.jpg}
    \caption{}
    \label{fig_graphlets}
\end{figure}
Recently, graphlet comparison has emerged as
a novel method for comparing large networks in
order to find local similarities in them. A
graph G is a pair $(V,E)$, where $V$ is a set of
vertices and $E \subseteq V\times V$ is a set of
edges. A connected graph is one where there is
a path between every pair of vertices.
Given a graph $G(V, E)$ and $S \subseteq V$,
then $G'(S, E')$ is a graphlet if and only if
it is connected $E' = \{(u, v) | u, v \in V \quad \&
\quad (u, v) \in E \rightarrow (u, v) \in E'\}$. 
There a total of 30 graphlets
of size 2, 3, and 5.  Figure \ref{fig_graphlets}
demonstrates these graphlets. 
As can be seen there is only one graphlet
of size 2 which is equivalent to an edge; that
is, the number of graphlet 1 in a graph is the
same as the number of edges on the graph. There
are also a total of 2 graphlets of size 2, 6
of size 4 and 20 of size 5. The nodes of each graphlet
can be partitioned into sets of topographically equivalent
nodes called orbits. For  example, in  Figure 
\ref{fig_graphlets}, we can see that G3 can be
partitioned into 2 sets of nodes, the middle ones
(white) and the outer nodes (black). 
For the same set of graphlets,
there are 73 orbits that are also illustrated in
figure  Figure using nodes of difference shades.
